\documentclass[12pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{array}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{caption}

\definecolor{hubteal}{HTML}{0F766E}
\definecolor{hubslate}{HTML}{0F172A}
\definecolor{hubgray}{HTML}{475569}
\definecolor{hubcode}{HTML}{F1F5F9}

\hypersetup{
    colorlinks=true,
    linkcolor=hubteal,
    urlcolor=hubteal,
    citecolor=hubteal
}

\lstdefinestyle{projectcode}{
    backgroundcolor=\color{hubcode},
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    framerule=0pt,
    xleftmargin=8pt,
    xrightmargin=8pt,
    aboveskip=10pt,
    belowskip=10pt
}
\lstset{style=projectcode}

\titleformat{\section}
  {\Large\bfseries\color{hubslate}}
  {\thesection}{0.8em}{}

\titleformat{\subsection}
  {\large\bfseries\color{hubteal}}
  {\thesubsection}{0.8em}{}

\titleformat{\subsubsection}
  {\normalsize\bfseries\color{hubslate}}
  {\thesubsubsection}{0.8em}{}

\pagestyle{fancy}
\fancyhf{}
\lhead{\textcolor{hubgray}{Electrical \& Computer Project Repository Hub}}
\rhead{\textcolor{hubgray}{Version 2.0.0 Stable}}
\cfoot{\thepage}

\setstretch{1.18}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

\begin{titlepage}
    \centering
    \vspace*{1.4cm}
    {\Huge\bfseries Electrical \& Computer Project Repository Hub\par}
    \vspace{0.35cm}
    {\Large Technical Documentation and Deployment Guide\par}
    \vspace{0.8cm}
    {\large Version 2.0.0 Stable Build\par}
    \vfill
    \begin{tabular}{rl}
        \textbf{Domain:} & Electrical and Computer project submissions \\
        \textbf{Frontend:} & React, Vite, Tailwind CSS \\
        \textbf{Backend:} & Node.js, Express.js \\
        \textbf{Storage:} & Official GitHub project repository \\
        \textbf{Workflow:} & Upload branch, pull request, auto-merge, auto-pull \\
        \textbf{Prepared By:} & Vaishnav Ceh \\
        \textbf{Creator Profile:} & \href{https://github.com/vaishnavceh}{github.com/vaishnavceh} \\
    \end{tabular}
    \vfill
    {\large \today\par}
\end{titlepage}

\tableofcontents
\newpage

\section{Executive Summary}

The Electrical \& Computer Project Repository Hub is a full-stack web platform for collecting, organizing, and publishing student project submissions. It replaces manual Git usage for students with a guided website upload flow. The backend receives project files, validates submission data, creates a GitHub upload branch, opens a pull request, and supports an automated workflow for merging accepted uploads.

The system is designed for department-level use. It separates website source code from student project storage, avoids exposing deployment endpoints on public pages, and keeps credentials only in backend environment variables.

\subsection{Current Version}

This document describes \textbf{version 2.0.0 stable build}. This version keeps the current deployment workflow ready for use, with in-site PDF documentation reading, live template file browsing, official storage repository operation, safe project overwrites, and cleaner generated README files.

\section{Version 2.0.0 Stable Update}

\subsection{Issues Solved}

\begin{itemize}[leftmargin=*]
    \item Team number validation now accepts \texttt{team-01} through \texttt{team-100}.
    \item Invalid team numbers such as \texttt{team-00}, \texttt{team-101}, \texttt{team-1}, and \texttt{team-001} are rejected.
    \item Students can now add optional additional comments to the generated \texttt{README.md}.
    \item Generated README files no longer contain unfinished placeholder instructions.
    \item README generation now attempts form input first, readable report PDF sections second, and safe fallback text after that.
    \item Existing project folders can now be replaced through a new upload pull request.
    \item Public pages no longer display the deployed backend server address.
    \item The project now supports the official Electrical and Computer GitHub storage repository.
    \item The Auto Merge GitHub Actions workflow is documented for the storage repository.
    \item Templates are now live in the official repository \texttt{TEMPLATES} folder.
\end{itemize}

\subsection{New Updates}

\begin{itemize}[leftmargin=*]
    \item Application version updated to \texttt{2.0.0 stable build}.
    \item Documentation now has its own tab with a click-to-load PDF.js preview inside the website.
    \item Templates page now lists the actual files and folders inside the official \texttt{TEMPLATES} directory.
    \item Creator GitHub profile is included in project information.
    \item Existing project uploads can replace previous folder contents through a new pull request.
    \item Generated README files use form input, readable report PDF sections, and safe fallback text.
    \item Know More page includes solved issues and stable build update notes.
    \item Upload page includes a Git command window for users familiar with Git.
    \item Admin Pane includes frontend and backend status checks behind a passkey.
    \item Templates page browses the official GitHub repository \texttt{TEMPLATES} directory inside the website.
    \item Light and dark mode are available in the frontend interface.
\end{itemize}

\section{Purpose and Scope}

\subsection{Purpose}

The purpose of this website is to make student project submission structured, repeatable, and easier to maintain. Students should not need to clone repositories, create branches, or open pull requests manually. The website handles the submission flow and lets GitHub workflows manage accepted project updates.

\subsection{Scope}

The platform supports:

\begin{itemize}[leftmargin=*]
    \item Team-based project submissions.
    \item Project files and optional report PDF uploads.
    \item Official course, seminar, lab, presentation, and review template access.
    \item Optional report and working-video links.
    \item Optional README comments.
    \item GitHub pull request creation.
    \item Auto-merge workflow support for upload branches.
    \item Repository browsing inside the website.
    \item Admin-only status checks.
\end{itemize}

The platform does not act as a complete learning management system. Authentication, role-based student accounts, grading, and analytics are future enhancements.

\section{Repository Strategy}

The project uses two separate repositories.

\begin{longtable}{p{0.28\linewidth} p{0.62\linewidth}}
\toprule
\textbf{Repository} & \textbf{Purpose} \\
\midrule
\texttt{ER\_Project-Hub} & Website source code, backend source code, frontend source code, documentation, Docker setup, and deployment configuration examples. \\
\texttt{ELECTRICAL-AND-COMPUTER-PROJECT-REPOSITORY-OFFICIAL} & Official storage location for accepted student project files. \\
\bottomrule
\end{longtable}

This separation keeps the website application clean and prevents student submissions from being mixed with source code.

\section{System Architecture}

\subsection{Architecture Overview}

\begin{center}
\begin{tabular}{>{\bfseries}p{0.25\linewidth} p{0.65\linewidth}}
\toprule
Layer & Responsibility \\
\midrule
Frontend & React/Vite application, student upload form, repository browser, admin pane, status UI, dark/light mode. \\
Backend & Express API, upload validation, file handling, GitHub branch creation, pull request creation, repository file listing. \\
GitHub Storage Repo & Stores accepted project files under batch, semester, subject, and team folders. \\
GitHub Actions & Auto-merge workflow for trusted upload branches after checks pass. \\
Deployment & Frontend and backend are deployed separately and connected using environment variables. \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Request Flow}

\begin{enumerate}[leftmargin=*]
    \item Student opens the frontend website.
    \item Student fills the upload form and selects files.
    \item Frontend sends form data to the configured backend service.
    \item Backend validates fields, filenames, and file safety rules.
    \item Backend creates an upload branch in the storage repository.
    \item If the same project folder already exists, backend deletes the old project files on the upload branch.
    \item Backend uploads project files and generated README content.
    \item Backend opens a pull request against \texttt{main}.
    \item GitHub Actions handles the auto-merge workflow for valid upload branches.
    \item Accepted files become visible through the repository browser.
\end{enumerate}

\section{Technology Stack}

\begin{longtable}{p{0.28\linewidth} p{0.62\linewidth}}
\toprule
\textbf{Technology} & \textbf{Use} \\
\midrule
React & Builds the browser-based user interface. \\
Vite & Provides fast development and optimized production builds. \\
Tailwind CSS & Provides utility-based styling and responsive layout. \\
Lucide React & Provides icons for navigation, buttons, status panels, and controls. \\
Node.js & Runtime for the backend service. \\
Express.js & API routing and middleware. \\
Multer & Handles multipart project file uploads. \\
Octokit & Communicates with the GitHub REST API. \\
Docker Compose & Supports local development and testing. \\
Vercel & Intended frontend deployment platform. \\
Node Web Service & Intended backend deployment environment. \\
\bottomrule
\end{longtable}

\section{Frontend Pages}

\subsection{Home}

The Home page summarizes the platform workflow. It tells users that project uploads are handled by the website, that auto-merge and auto-pull are enabled after checks pass, and that concerns should be reported to the admin. Documentation is available from its own navigation tab so the Home page does not automatically load the PDF.

\subsection{Documentation}

The Documentation page provides a click-to-load PDF.js preview of the latest compiled PDF documentation. The PDF is loaded only after the user requests the preview, which prevents the Home page from triggering an automatic browser download and avoids relying on blocked Google Docs embedding.

\subsection{Upload Project}

The Upload Project page is the main student submission page. It collects:

\begin{itemize}[leftmargin=*]
    \item Batch year, for example \texttt{batch-2027}.
    \item Semester, for example \texttt{semester-5}.
    \item Subject, for example \texttt{dbms}.
    \item Team number from \texttt{team-01} through \texttt{team-100}.
    \item Project name, for example \texttt{library-management}.
    \item Team members.
    \item Project description.
    \item Tools used.
    \item Technologies used.
    \item Sources or references used.
    \item Problem statement, optional. If omitted, the README derives it from the project description.
    \item Installation or setup instructions, optional.
    \item Steps to run or test, optional.
    \item Screenshots, photos, or demo output notes, optional.
    \item Presentation details, optional.
    \item Future improvements, optional.
    \item Additional README comments, optional.
    \item Project files.
    \item Project report PDF, optional.
    \item Google Drive report link, optional.
    \item Working video link, optional.
\end{itemize}

After upload, the page shows the created branch, pull request link, project path, and Git process window.
If the upload replaces an existing project folder, the success panel reports how many existing files were replaced.

\subsection{Files}

The Files page lets users browse accepted project files from the official storage repository inside the website. It does not expose GitHub tokens or backend secrets.

\subsection{Guidelines}

The Guidelines page explains upload expectations. It clarifies that students should submit through the website and that normal uploads are handled by the automated workflow after checks pass.

\subsection{Repository}

The Repository page explains the required storage folder structure:

\begin{lstlisting}
batches/{batch}/{semester}/{subject}/{team-number}-{project-name}/
\end{lstlisting}

Example:

\begin{lstlisting}
batches/batch-2027/semester-5/dbms/team-01-library-management/
\end{lstlisting}

\subsection{README Requirements}

The README page explains what a useful project README should contain. The backend generates a starter README from form data, and students can add optional comments for special setup notes, hardware warnings, known issues, or extra context.

\subsection{Hardware}

The Hardware page gives guidance for electronics, electrical, embedded systems, IoT, robotics, and hardware projects. Students are encouraged to include circuit diagrams, source code, reports, simulation files, photos, and demo evidence.

\subsection{Rules}

The Rules page defines safe submission behavior. Students must not upload secrets, tokens, passwords, private keys, unrelated private data, or unsafe executable files.

\subsection{Templates and Resources}

This page shows the actual files and folders from the live official \texttt{TEMPLATES} directory in the storage repository. Students can open template folders, view template file names, open files on GitHub, and download available files before preparing their submissions.

Official templates repository:

\begin{lstlisting}
https://github.com/ELECTRICAL-AND-COMPUTER-TKMCE/ELECTRICAL-AND-COMPUTER-PROJECT-REPOSITORY-OFFICIAL
\end{lstlisting}

Official templates folder:

\begin{lstlisting}
https://github.com/ELECTRICAL-AND-COMPUTER-TKMCE/ELECTRICAL-AND-COMPUTER-PROJECT-REPOSITORY-OFFICIAL/tree/main/TEMPLATES
\end{lstlisting}

\subsection{Know More}

The Know More page shows version information, workflow status, solved issues, operational notes, and planned features.
It also includes the creator GitHub profile:

\begin{lstlisting}
https://github.com/vaishnavceh
\end{lstlisting}

\section{Admin Pane}

The Admin Pane is located in the lower area of the Home page. It is protected by passkeys configured through frontend environment variables.

\subsection{Admin Features}

\begin{itemize}[leftmargin=*]
    \item Frontend status check.
    \item Backend/project service status check.
    \item Runtime configuration check.
    \item Repository access check.
    \item Expandable command/process log.
\end{itemize}

\subsection{Passkey Configuration}

The frontend reads the admin passkey from:

\begin{lstlisting}
VITE_ADMIN_PASSKEY=<admin-passkey>
\end{lstlisting}

Multiple passkeys can be supported with:

\begin{lstlisting}
VITE_ADMIN_PASSKEYS=<passkey-one>,<passkey-two>
\end{lstlisting}

\section{Upload Validation Rules}

\subsection{Required Fields}

\begin{itemize}[leftmargin=*]
    \item Batch year.
    \item Semester.
    \item Subject.
    \item Team number.
    \item Project name.
    \item Team members.
    \item Project description.
    \item Tools used.
    \item Technologies used.
    \item Sources or references used.
    \item Project type.
    \item Confirmation checkbox.
\end{itemize}

\subsection{Team Number Rule}

Valid examples:

\begin{lstlisting}
team-01
team-09
team-10
team-99
team-100
\end{lstlisting}

Invalid examples:

\begin{lstlisting}
team-00
team-101
team-1
team-001
\end{lstlisting}

\subsection{Blocked Uploads}

The backend blocks filenames that appear unsafe, including executable files, private key files, environment files, token files, credential files, and path traversal attempts.

\section{Generated README.md}

For each project, the backend creates a starter \texttt{README.md}. It includes:

\begin{itemize}[leftmargin=*]
    \item Project title.
    \item Team members.
    \item Batch, semester, subject, project type, and team folder.
    \item Project description.
    \item Tools used.
    \item Technologies used.
    \item Sources or references.
    \item Project file location.
    \item Report PDF status.
    \item Optional report link.
    \item Optional working video link.
    \item Optional additional comments.
    \item \texttt{Not available.} for optional sections that are not provided and cannot be read from the report PDF.
\end{itemize}

\section{Overwrite Behavior}

When a team uploads a project to the same batch, semester, subject, team number, and project name path, the backend no longer rejects it as a duplicate. Instead, it creates an upload branch from the latest \texttt{main}, removes the existing files in that project folder on the upload branch, uploads the new files, and opens a pull request.

This means the replacement is still tracked by Git history. After the pull request is auto-merged, users can run \texttt{git pull origin main} in the storage repository to receive the overwritten project folder.

\section{GitHub Actions Auto-Merge Workflow}

The Auto Merge workflow must be created in the official storage repository, not in the website source repository.

File path:

\begin{lstlisting}
.github/workflows/auto-merge-student-uploads.yml
\end{lstlisting}

Workflow:

\begin{lstlisting}
name: Auto merge student uploads

on:
  pull_request:
    types: [opened, synchronize, reopened, ready_for_review]
    branches:
      - main

permissions:
  contents: write
  pull-requests: write

jobs:
  auto-merge:
    if: startsWith(github.head_ref, 'upload/')
    runs-on: ubuntu-latest

    steps:
      - name: Auto merge upload pull request
        run: gh pr merge "$PR_URL" --squash --auto --delete-branch
        env:
          GH_TOKEN: ${{ secrets.GITHUB_TOKEN }}
          PR_URL: ${{ github.event.pull_request.html_url }}
\end{lstlisting}

\subsection{Workflow Settings}

In the storage repository, configure:

\begin{itemize}[leftmargin=*]
    \item \textbf{Settings} $\rightarrow$ \textbf{Actions} $\rightarrow$ \textbf{General}.
    \item Enable \textbf{Read and write permissions}.
    \item Enable \textbf{Allow GitHub Actions to create and approve pull requests}.
\end{itemize}

The workflow only applies to branches that start with \texttt{upload/}. Normal manual pull requests are not auto-merged by this rule.

\section{Environment Variables}

\subsection{Frontend}

\begin{lstlisting}
VITE_API_BASE_URL=<configured-project-service-url>
VITE_ADMIN_PASSKEY=<admin-passkey>
VITE_STORAGE_REPOSITORY_URL=https://github.com/ELECTRICAL-AND-COMPUTER-TKMCE/ELECTRICAL-AND-COMPUTER-PROJECT-REPOSITORY-OFFICIAL.git
\end{lstlisting}

\textbf{Note:} The deployed project service URL should be configured in Vercel or local environment files. It should not be hardcoded into committed source files.

\subsection{Backend}

\begin{lstlisting}
GITHUB_OWNER=ELECTRICAL-AND-COMPUTER-TKMCE
GITHUB_REPO=ELECTRICAL-AND-COMPUTER-PROJECT-REPOSITORY-OFFICIAL
GITHUB_BASE_BRANCH=main
GITHUB_TOKEN=<server-side-token>
FRONTEND_URL=<frontend-origin>
CORS_ORIGIN=<frontend-origin>
NODE_ENV=production
PORT=10000
\end{lstlisting}

\textbf{Important:} The GitHub token must never be placed in frontend code, public screenshots, documentation, or Git history.

\section{Deployment Guide}

\subsection{Frontend Deployment}

The frontend can be deployed to Vercel.

\begin{enumerate}[leftmargin=*]
    \item Import the website source repository into Vercel.
    \item Set the frontend root directory if required.
    \item Add the frontend environment variables.
    \item Deploy the frontend.
    \item Copy the final frontend origin.
    \item Update backend CORS settings with the final frontend origin.
\end{enumerate}

\subsection{Backend Deployment}

The backend should run as a Node web service.

\begin{lstlisting}
npm install
npm start
\end{lstlisting}

Backend health check path:

\begin{lstlisting}
/api/health
\end{lstlisting}

Routes such as \texttt{/} or \texttt{/api} may return \texttt{Cannot GET} if not defined. That is acceptable when \texttt{/api/health} returns a valid health response.

\section{Testing Checklist}

\begin{longtable}{p{0.08\linewidth} p{0.72\linewidth} p{0.12\linewidth}}
\toprule
\textbf{No.} & \textbf{Test Item} & \textbf{Status} \\
\midrule
1 & Frontend loads successfully. & Pending \\
2 & Light mode and dark mode work correctly. & Pending \\
3 & Admin Pane login works with configured passkey. & Pending \\
4 & Backend health status check works from Admin Pane. & Pending \\
5 & Upload form accepts \texttt{team-01} through \texttt{team-100}. & Pending \\
6 & Upload form rejects invalid team numbers. & Pending \\
7 & Optional README comments appear in generated \texttt{README.md}. & Pending \\
8 & Backend creates an upload branch in the official storage repository. & Pending \\
9 & Backend opens a pull request against \texttt{main}. & Pending \\
10 & GitHub Actions auto-merge workflow runs for \texttt{upload/} branches. & Pending \\
11 & Accepted project files appear in the repository browser. & Pending \\
\bottomrule
\end{longtable}

\section{Security Notes}

\begin{itemize}[leftmargin=*]
    \item Store GitHub tokens only in backend environment variables.
    \item Never commit \texttt{.env} files.
    \item Rotate any token that was shown in a screenshot, browser page, terminal, or chat.
    \item Use the minimum GitHub permissions required for contents and pull requests.
    \item Prefer a department bot account or GitHub App for long-term deployment.
    \item Keep backend deployment endpoints out of public website pages.
    \item Do not allow students to submit passwords, API keys, private keys, or secret files.
\end{itemize}

\section{Troubleshooting}

\begin{longtable}{p{0.32\linewidth} p{0.58\linewidth}}
\toprule
\textbf{Problem} & \textbf{Likely Fix} \\
\midrule
Frontend says backend is not reachable & Check frontend environment variable \texttt{VITE\_API\_BASE\_URL}, backend CORS origin, and backend service status. \\
Upload fails with team number error & Use \texttt{team-01} through \texttt{team-100}. \\
Pull request is created but not merged & Check GitHub Actions permissions and confirm the branch starts with \texttt{upload/}. \\
Repository browser does not show files & Confirm backend environment points to the official storage repository and token has access. \\
Admin Pane login fails & Confirm \texttt{VITE\_ADMIN\_PASSKEY} or \texttt{VITE\_ADMIN\_PASSKEYS} is configured and redeploy frontend. \\
\bottomrule
\end{longtable}

\section{Future Enhancements}

\begin{itemize}[leftmargin=*]
    \item Student login and team submission history.
    \item Admin dashboard for accepted uploads and rejected submissions.
    \item Search and filters by batch, semester, subject, team, and technology.
    \item More detailed GitHub Actions status inside the website.
    \item Course material templates, seminar templates, report templates, and lab resources.
    \item Department-level project analytics.
\end{itemize}

\section{Conclusion}

The Electrical \& Computer Project Repository Hub provides a structured and safer workflow for collecting department project submissions. Version 2.0.0 stable build improves validation, documentation, official repository configuration, in-site PDF documentation reading, visible template directory browsing, generated README flexibility, overwrite handling, and deployment readiness. The system is prepared for frontend hosting, backend production use, and official storage repository testing.

\end{document}
